Verifying Demonstrations

### 2018-11-29 paper/protocol.tex

We now present \CROCUS, a protocol for privately verifyiable crowd counts.
The protocol consists of five phases: setup (in \cref{ProtocolSetup}),
join, participation, submission (all in in \cref{ProtocolDuring} ) and
verification (in \cref{ProtocolVerification}).

>>>>

We now present \CROCUS, a protocol for privately verifyiable crowd counts.
The protocol consists of five phases: setup (in \cref{ProtocolSetup}),
join, participation, submission (all in in \cref{ProtocolDuring}) and
verification (in \cref{ProtocolVerification}).
